Nested sampling with two objective functions

### 2016-01-27 Paper/ms.tex
Rob

% Authors (Add full first names)
\Author{Brendon J. Brewer$^{1,}$* and Ewan Cameron$^{2}$}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ Department of Statistics, The University of Auckland, Private Bag 92019,
Auckland 1142, New Zealand\\
$^{2}$ Spatial Ecology and Epidemiology Group, Tinbergen Building, Department
of Zoology, University of Oxford, South Parks Road, Oxford, UK}

@@

\section{Test problem}

We tested the algorithm on a simple 100-dimensional example, where the
prior is a uniform distribution between 0 and 1 for each coordinate:
\begin{eqnarray}
\pi(\xx) &=& \prod_{i=1}^{100}
\left\{
\begin{array}{lr}
1, & x_i \in [0, 1]\\
0, & \textnormal{otherwise.}
\end{array}
\right.
\end{eqnarray}
The first objective function is quadratic in form, such that the canonical
distribution is an iid gaussian centered at $(0.5, 0.5, ..., 0.5)$:
\begin{eqnarray}
L_1(\xx) &=& -\sum_{i=1}^{100} \left(x_i - 0.5\right)^2.
\end{eqnarray}

@@

@@

It is a pleasure to thank Gábor Csányi (Cambridge), Livia B. Pártay (Cambridge),
Robert Baldock (Cambridge), and Will Handley (Cambridge)
for valuable conversations.

>>>>

% Authors (Add full first names)
\Author{Brendon J. Brewer$^{1,}$*, Ewan Cameron$^{2}$, and
Robert J. N. Baldock$^{3}$}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ Department of Statistics, The University of Auckland, Private Bag 92019,
Auckland 1142, New Zealand\\
$^{2}$ Spatial Ecology and Epidemiology Group, Tinbergen Building, Department
of Zoology, University of Oxford, South Parks Road, Oxford, UK\\
$^{3}$ Cavendish, University of Cambridge, Cambridge, UK}

@@

\section{Example 1: Known solution}
We tested the algorithm on a simple 100-dimensional example, where the
prior is a uniform distribution between 0 and 1 for each coordinate:
\begin{eqnarray}
\pi(\xx) &=& \prod_{i=1}^{100}
\left\{
\begin{array}{lr}
1, & x_i \in [0, 1]\\
0, & \textnormal{otherwise.}
\end{array}
\right.
\end{eqnarray}
The first objective function is quadratic in form, such that the canonical
distribution is an iid gaussian centered at $(0.5, 0.5, ..., 0.5)$:
\begin{eqnarray}
L_1(\xx) &=& -\sum_{i=1}^{100} \left(x_i - 0.5\right)^2.
\end{eqnarray}

@@

\section{Example 2: Lennard-Jones/Polymer Example}

\section{Example 3: ``MaxEnt'' image deconvolution example}

@@

It is a pleasure to thank Gábor Csányi (Cambridge), Livia B. Pártay (Cambridge),
and Will Handley (Cambridge)
for valuable conversations.
